TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
Conclusion

The tests conducted with the algorithms have two environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions \cite{linux-netem}. \texttt{netem} is applied to the incoming side of the interfaces of the clients to emulate the same packet loss and delay. Windows, which is tested as a server, does not support \texttt{netem}. Therefore the packet loss and delay are applied to the incoming interfaces of the clients. Packet loss and delay are chosen as the behavior of most TCP algorithms depends on those variables \cite{bbr-congestion}\cite{bic-tcp-congestion}\cite{compound-tcp-congestion}\cite{cubic-tcp-congestion}\cite{dctcp-congestion}. The values for the environment variables are chosen based on measurements performed by Verizon \cite{verizon-latency}.

@@

The results have shown that the current default TCP congestion control algorithms are showing fair behavior: The bandwidth is allocated equally among all nodes. Therefore, currently no traffic control is needed, unless someone would create an unfair TCP congestion control algorithm. This can, after more research, be detected by one of the monitoring solutions proposed in this paper. As for the tested TCP congestion control algorithms, there is no impact on the service and availability for customers when using those algorithms mixed in one environment.

The BBR congestion control algorithm performs best when delay and loss occur of all TCP congestion control algorithms tested. DCTCP is only suitable when both the server and client are in the same datacenter, because the start up of the connection is slow when congestion in the network occurs. For datacenters it works well, because it keeps the queue lengths to a minimum, assuring a packet arrives at its destination.
\end{enumerate}

>>>>

The tests conducted with the algorithms have two environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions \cite{linux-netem}. \texttt{netem} is applied to the incoming side of the interfaces of the clients to emulate the same packet loss and delay. Windows, which is tested as a server, does not support \texttt{netem}. Therefore the packet loss and delay are applied to the incoming interfaces of the clients. Packet loss and delay are chosen as the behavior of most TCP algorithms depends on those variables [TODO: SRC]. The values for the environment variables are chosen based on measurements performed by Verizon \cite{verizon-latency}.

@@

For the algorithms BIC, BBR, CUBIC and DCTCP, we conclude that they allocate
bandwidth fairly and do not suppress each other. There is no impact on the
service for customers when using those algorithms mixed in one environment.

CTCP, the default algorithm for Microsoft Windows, shows inconclusive results
and we can not draw any conclusions with regards to this algorithm.

In our results, BBR shows better performance than any other algorithm when
packet loss occurs. Finally, DCTCP is only suitable when both the server and
client are in the same datacenter. There is a considerable ramp-up time when
congestion occurs. Within datacenters this works well, because with no
congestion it keeps the queue lengths to a minimum.
